---
title: "vgt_stgt_Study1_outcome_fixations"
author: "Mariya Cherkasova"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load packages

```{r,include=FALSE}
rm(list=ls()) #clear env
library(readr)
library(lme4)
library(lattice)
library(lmerTest)
library(emmeans)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(influence.ME)
library(gmodels)#CI
library(corrplot)
library(arm)
library(gridExtra)
library(sjPlot)
library(brms)
library(report)
```

Load data

```{r, include=FALSE}
STGT_tertiary_splitJN <- read_csv("STGT_CSplus2_tertiary_splitJN.csv")
fbFixC <- read_csv("JN_cued_group2_fix_feedback.csv")
fbFixUC <- read_csv("JN_uncued_group1_fix_feedback.csv")

# ptdt imports as chr, fix that
fbFixC$ptdt <- as.numeric(fbFixC$ptdt)
fbFixUC$ptdt <- as.numeric(fbFixUC$ptdt)

fbFixC$ptdt[is.na(fbFixC$ptdt)] <- 0
fbFixUC$ptdt[is.na(fbFixUC$ptdt)] <- 0
fbFixUC$id[is.na(fbFixUC$id)] <- 114
fbFixC$id[fbFixC$id==427] <- 127

```

Participant-wise % dwell time summaries for cued

```{r, include=FALSE}
fbFixC_summ <- fbFixC %>% 
  group_by(id,ia) %>% 
  summarise_each(funs(mean)) %>% 
  dplyr::select(!(trial)) %>% 
  pivot_wider(names_from = ia, values_from = c(dt,ptdt)) %>% 
  mutate(gazeidx_fb=ptdt_coins-ptdt_total)
fbFixC_summ$cues <- rep("cued",68)

histogram(fbFixC_summ$gazeidx_fb)
```

Participant-wise % dwell time summaries for uncued

```{r}
fbFixUC_summ <- fbFixUC %>% 
  group_by(id,ia) %>% 
  summarise_each(funs(mean)) %>% 
  dplyr::select(!(trial)) %>% 
  pivot_wider(names_from = ia, values_from = c(dt,ptdt)) %>% 
  mutate(gazeidx_fb=ptdt_coins-ptdt_total) 
fbFixUC_summ$cues <- rep("uncued",63)

histogram(fbFixUC_summ$gazeidx_fb)
```

Merge with STGT with feedback fixation data.

```{r}
fbFixC_summ$id <- as.character(fbFixC_summ$id)
STGT_tertiary_splitJN$id <- as.character(STGT_tertiary_splitJN$id)
fbFix <- rbind(fbFixUC_summ,fbFixC_summ)
fbFix_stgt <- inner_join(fbFix, STGT_tertiary_splitJN,by="id")

```

Look at plots, run regressions
Participants look at the feedback location more in the cued condition  but no interaction with gazeidx (phenotype)

```{r}
ml <- lm(gazeidx_fb~gazeidx*cues,data=fbFix_stgt)
summary(ml)

ggplot(fbFix_stgt, aes(x=gazeidx, y=gazeidx_fb,color=cues,fill=cues))+
       geom_point()+geom_smooth()

ggplot(fbFix_stgt, aes(x=STGT_ter, y=gazeidx_fb,color=cues,fill=cues))+
       geom_boxplot()
```

Bayesian regression


```{r}

bayesian_ml <- brm(gazeidx_fb~gazeidx*cues,data=fbFix_stgt, family=gaussian, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000)
summary(bayesian_ml)
bm_tab <- report_table(bayesian_ml)
bm_tab

# without gaze index or interaction with cues
bayesian_gazeidxNull <- brm(gazeidx_fb~cues,data=fbFix_stgt, family=gaussian, save_pars = save_pars(all = TRUE), sample_prior = TRUE, iter = 10000)
summary(bayesian_gazeidxNull)
bm_tab_null <- report_table(bayesian_gazeidxNull)
bm_tab_null

full_null = bayes_factor(bayesian_ml, bayesian_gazeidxNull)
full_null

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
